Contextual Combinatorial Cascading Bandits

### 2016-01-08 experiment/experiment.tex
fixed minor exp doc

Let $E=\{e_1,...,e_L\}$ be the set of arms, and $x_{i,t}$ be the context associated with arm $e_i$ at time $t$.
In order to send a package from $u_t$ to $v_t$,
the agent have to choose an superarm from $$S=\{A=(e_{k_1},...,e_{k_n}):e_{k_j}\in E, e_{k_1},...,e_{k_n} \text{is a simple path of } G \text{ from } u_t \text{ to } v_t\},$$
with the expected payoffs (opt out discount) $$E[r_A|\theta]=\Pi_{1\leq i\leq n(A)}(1-\exp(-\tau/(1-\theta^{\top}x_{k(A)_i,t}))),$$
where $n(A)$ and $k(A)_i$ are the amount of arms in superarm $A$, and the index of the $i$-th arm, separately.
The agent finds $A_t$ by running shortest path algorithm on $G$ with weight $\hat{\theta}^{\top}x_{k_i,t}$ assigned to $e_i$, which yields $$A_t=\argmin_{A\in S}\sum_{1\leq i\leq n(A)}\hat{\theta}^{\top}x_{k(A)_i,t}.$$
For $A\in S$, denote $\hat{\mu}(A)_i=1-\hat{\theta}^{\top}x_{k(A_t)_i,t},$ we have then 
\begin{align*}
  E[r_{A_t}|\hat{\theta}]/E[r_A|\hat{\theta}] &= \frac{\Pi_{1\leq i\leq n(A_t)}(1-e^{-\tau/\hat{\mu}(A_t)_i})}{\Pi_{1\leq i\leq n(A)}(1-e^{-\tau/\hat{\mu}(A)_i})}\\
  &\geq \min_{0\leq \sigma \leq n(A), \sum_i \hat{\mu}(A_t)_i=\sum_i \hat{\mu}(A)_i=\sigma}\frac{\Pi_{1\leq i\leq n(A_t)}(1-e^{-\tau/\hat{\mu}(A_t)_i})}{\Pi_{1\leq i\leq n(A)}(1-e^{-\tau/\hat{\mu}(A)_i})}\\
  &\geq \min_{0\leq \sigma \leq n(A)}\frac{(1-e^{-\tau})^\sigma}{(1-e^{-\tau n(A)/\sigma})^{n(A)}}\\
  &\geq \min_{0\leq \sigma \leq n(A)}\frac{1-e^{-\tau/\sigma}}{(1-e^{-\tau n(A)/\sigma})^{n(A)}}\\
  &\geq 1-e^{-\tau/n(A)}/(1-e^{-\tau})^{n(A)}\\
  &\geq (1-e^{-\tau/|V|})/(1-e^{-\tau})^{|V|}.\\
\end{align*}
Let $\alpha(\tau, G)=(1-e^{-\tau/|V|})/(1-e^{-\tau})^{|V|}$, the above inequality shows that we can realize the $\alpha(\tau, G)$-approximation oracle using shortest path algorithm.
After the agent chooses the shortest path as the superarm, the reward and the first ever edge with high latency, if any, is feedbacked.

>>>>

Let $E=\{e_1,...,e_L\}$ be the set of arms, and $x_{i,t}$ be the context associated with arm $e_i$ at time $t$.
In order to send a package from $u_t$ to $v_t$,
the agent have to choose an superarm from $$S=\{A=(e_{k_1},...,e_{k_n}):e_{k_j}\in E, e_{k_1},...,e_{k_n} \text{is a simple path of } G \text{ from } u_t \text{ to } v_t\},$$
with the expected payoffs (opt out discount) $$E[r_A|\theta]=\Pi_{1\leq i\leq n(A)}(1-\exp(-\tau/(1-\theta^{\top}x_{k(A)_i,t}))),$$
where $n(A)$ and $k(A)_i$ are the amount of arms in superarm $A$, and the index of the $i$-th arm, separately.
The agent finds $A_t$ by running shortest path algorithm on $G$ with weight $\hat{\theta}^{\top}x_{k_i,t}$ assigned to $e_i$, which yields $$A_t=\argmin_{A\in S}\sum_{1\leq i\leq n(A)}\hat{\theta}^{\top}x_{k(A)_i,t}.$$
For $A\in S$, denote $\hat{\mu}(A)_i=1-\hat{\theta}^{\top}x_{k(A)_i,t},$ we have then 
\begin{align*}
  E[r_{A_t}|\hat{\theta}]/E[r_A|\hat{\theta}] &= \frac{\Pi_{1\leq i\leq n(A_t)}(1-e^{-\tau/\hat{\mu}(A_t)_i})}{\Pi_{1\leq i\leq n(A)}(1-e^{-\tau/\hat{\mu}(A)_i})}\\
  &\geq \min_{0\leq \sigma \leq n(A), \sum_i \hat{\mu}(A_t)_i=\sum_i \hat{\mu}(A)_i=\sigma}\frac{\Pi_{1\leq i\leq n(A_t)}(1-e^{-\tau/\hat{\mu}(A_t)_i})}{\Pi_{1\leq i\leq n(A)}(1-e^{-\tau/\hat{\mu}(A)_i})}\\
  &\geq \min_{0\leq \sigma \leq n(A)}\frac{(1-e^{-\tau})^\sigma}{(1-e^{-\tau n(A)/\sigma})^{n(A)}}\\
  &\geq \min_{0\leq \sigma \leq n(A)}\frac{1-e^{-\tau/\sigma}}{(1-e^{-\tau n(A)/\sigma})^{n(A)}}\\
  &\geq 1-e^{-\tau/n(A)}/(1-e^{-\tau})^{n(A)}\\
  &\geq (1-e^{-\tau/|V|})/(1-e^{-\tau})^{|V|}.\\
\end{align*}
Let $\alpha(\tau, G)=(1-e^{-\tau/|V|})/(1-e^{-\tau})^{|V|}$, the above inequality shows that we can realize the $\alpha(\tau, G)$-approximation oracle using shortest path algorithm.
After the agent chooses the shortest path as the superarm, the reward and the first ever edge with high latency, if any, is feedbacked.
